\pagestyle{fancy} % Enable fancy page style

% Clear default header and footer
\fancyhf{}

% Set left footer to Roman page number
\fancyfoot[R]{\thepage} % Right footer

% Set left footer to custom text
\fancyfoot[L]{BEProjectReportCP5For2025} % Left footer

% Set header with title
\fancyhead[L]{AUTOMOTIVE DIAGNOSTIC AND ACTIVITY MONITORING (ADAM) SYSTEM}

% Disable the horizontal line under the header
\renewcommand{\headrulewidth}{0pt}

\newpage
\pagenumbering{roman} % Start page numbering in Roman numerals
\setcounter{page}{1} % Begin numbering from page 1
\chapter*{\centering  ACKNOWLEDGMENT}
\addcontentsline{toc}{chapter}{Acknowledgment}
% \begin{center}
% \textbf{\LARGE ACKNOWLEDGMENT}\\[1cm]
% \end{center}
% \begin{center}
\justify

We take this opportunity to whole-heartedly thank those who were instrumental in helping us achieve our goals. We extend our heartfelt gratitude to our Principal, \textbf{Dr. Mahesh Parappagoudar}, for his unwavering support and encouragement throughout the duration of this project. His visionary leadership and constant motivation have been invaluable to us. 

We are equally grateful to our Head of Department, \textbf{Dr. Supriya Patil}, for providing us with the necessary resources, facilities, and guidance that played a crucial role in the successful completion of our work. We would like to express our deepest appreciation to our project guide, \textbf{Vijaykumar Naik Pawar}, whose insightful suggestions, constructive feedback, and dedicated support were instrumental in shaping this project. Their expertise and constant encouragement inspired us to push our limits and achieve the desired outcomes.

We would also like to thank the staff of the \textbf{Department of Computer Engineering} for their cooperation and support. We also wish to acknowledge the valuable contributions of the faculty members, whose knowledge and guidance have enriched our understanding throughout the course of this endeavour. Additionally, we are thankful to our peers and friends for their encouragement, collaboration, and constructive feedback, which motivated us to refine our work and strive for excellence.
