\newpage
\chapter{BIBLIOGRAPHY}

\begin{enumerate}
    \item Duy Le Nguyen, Myung-Eui Lee and A. Lensky, \textbf{"The design and implementation of new Vehicle Black Box using the OBD information,"} \textit{2012 7th International Conference on Computing and Convergence Technology (ICCCT)}, Seoul, Korea (South), 2012, pp. 1281-1284.

    \item P. R. Sawant and Y. B. Mane, \textbf{"Design and Development of On-Board Diagnostic (OBD) Device for Cars,"} \textit{2018 Fourth International Conference on Computing Communication Control and Automation (ICCUBEA)}, Pune, India, 2018, pp. 1-4, \url{https://doi.org/10.1109/ICCUBEA.2018.8697833}.

    \item R. Malekian, N. R. Moloisane, L. Nair, B. T. Maharaj and U. A. K. Chude-Okonkwo, \textbf{"Design and Implementation of a Wireless OBD II Fleet Management System,"} \textit{IEEE Sensors Journal}, vol. 17, no. 4, pp. 1154-1164, Feb. 15, 2017, \url{https://doi.org/10.1109/JSEN.2016.2631542}.

    \item Landry Frank Ineza Havugimana, Bolan Liu, Fanshuo Liu, Junwei Zhang, Ben Li and Peng Wan, \textbf{"Review of Artificial Intelligent Algorithms for Engine Performance, Control, and Diagnosis,"} \textit{Energies}, vol. 16, 2023, pp. 1206,\\ \url{https://doi.org/10.3390/en16031206}.

    \item R. Ahmed, M. El Sayed, S. A. Gadsden, J. Tjong and S. Habibi, \textbf{"Automotive Internal-Combustion-Engine Fault Detection and Classification Using Artificial Neural Network Techniques,"} \textit{IEEE Transactions on Vehicular Technology}, vol. 64, no. 1, pp. 21-33, Jan. 2015,\\ \url{https://doi.org/10.1109/TVT.2014.2317736}.

    \item J. B. Porch, C. Heng Foh, H. Farooq and A. Imran, \textbf{"Machine Learning Approach for Automatic Fault Detection and Diagnosis in Cellular Networks,"} \textit{2020 IEEE International Black Sea Conference on Communications and Networking (BlackSeaCom)}, Odessa, Ukraine, 2020, pp. 1-5,\\ \url{https://doi.org/10.1109/BlackSeaCom48709.2020.9234962}.

    \item S. N. Narayanan, S. Mittal and A. Joshi, \textbf{"OBD\_SecureAlert: An Anomaly Detection System for Vehicles,"} \textit{2016 IEEE International Conference on Smart Computing (SMARTCOMP)}, St. Louis, MO, USA, 2016, pp. 1-6,\\ \url{https://doi.org/10.1109/SMARTCOMP.2016.7501710}.

    \item J. E. Meseguer, C. T. Calafate, J. C. Cano and P. Manzoni, \textbf{"Assessing the impact of driving behavior on instantaneous fuel consumption,"} \textit{2015 12th Annual IEEE Consumer Communications and Networking Conference (CCNC)}, Las Vegas, NV, USA, 2015, pp. 443-448, \url{https://doi.org/10.1109/CCNC.2015.7158016}.

    \item R. Massoud, F. Bellotti, R. Berta, A. De Gloria and S. Poslad, \textbf{"Exploring Fuzzy Logic and Random Forest for Car Drivers’ Fuel Consumption Estimation in IoT-Enabled Serious Games,"} \textit{2019 IEEE 14th International Symposium on Autonomous Decentralized System (ISADS)}, Utrecht, Netherlands, 2019, pp. 1-7, \url{https://doi.org/10.1109/ISADS45777.2019.9155706}.

    \item T. Liu, G. Yang and D. Shi, \textbf{"Construction of Driving Behavior Scoring Model based on OBD Terminal Data Analysis,"} \textit{2020 5th International Conference on Information Science, Computer Technology and Transportation (ISCTT)}, Shenyang, China, 2020, pp. 24-27, \url{https://doi.org/10.1109/ISCTT51595.2020.00012}.
\end{enumerate}
