\chapter{REQUIREMENTS}
\justify

\section{Functional Requirements}
Functional requirements define the specific operations and functionalities the ADAM System must perform under various conditions. These include:

\begin{enumerate}
    \item \textbf{Real-Time Data Collection:}
    \begin{itemize}
        \item Continuously retrieve and store data such as RPM, speed, engine temperature, and throttle position from the OBD-II interface.
        \item Ensure secure and uninterrupted data transmission to the processing unit.
    \end{itemize}

    \item \textbf{Black Box Functionality:}
    \begin{itemize}
        \item Record and retain critical vehicle parameters during regular operation and immediately preceding an accident.
        \item Enable playback or export of stored data for analysis and forensic purposes.
    \end{itemize}
    \item \textbf{Mobile Application Features:}
    \begin{itemize}
        \item Provide real-time visualizations of vehicle performance and health metrics.
        \item Alert users to diagnostic issues and suggest maintenance actions.
        \item Support CSV export of forensic data for law enforcement or insurance purposes.
    \end{itemize}
    \item \textbf{Driving Pattern Analysis:}
    \begin{itemize}
        \item Collect and analyze driving behavior, including acceleration, braking, and speed trends.
        \item Provide feedback for users, insurers, and government agencies to improve safety and policy planning.
    \end{itemize}
    \item \textbf{Forensic Data Sharing:}
    \begin{itemize}
        \item Enable encrypted sharing of critical data with third parties, ensuring compliance with privacy standards.
    \end{itemize}
\end{enumerate}

\section{Other Nonfunctional Requirements}
Nonfunctional requirements describe the system's expected performance and quality attributes. These include:

\begin{enumerate}
    \item \textbf{Reliability:}
    \begin{itemize}
        \item Ensure 99.9% uptime for data collection and processing components.
        \item Implement fail-safe mechanisms for data storage to prevent loss during system failure.
    \end{itemize}
    \item \textbf{Security:}
    \begin{itemize}
        \item Encrypt all stored and transmitted data to protect sensitive user and  vehicle information. 
        \item Restrict access to authorized personnel or applications only.
    \end{itemize}
    \item \textbf{Performance:}
    \begin{itemize}
        \item Process and analyze real-time data within 1 second of retrieval.
        \item Maintain seamless interaction between the mobile app and backend systems with minimal latency.
    \end{itemize}
    \item \textbf{Maintainability:}
    \begin{itemize}
        \item Design modular software components to facilitate updates and bug fixes.
        \item Provide comprehensive documentation for developers and users.
    \end{itemize}
    \item \textbf{Scalability:}
    \begin{itemize}
        \item Support integration with diverse vehicle models and OBD-II protocols.
        \item Ensure compatibility with additional sensors and third-party services in future expansions.
    \end{itemize}
\end{enumerate}

\section{Hardware Requirements}
The hardware required to develop and deploy the ADAM System includes:
\begin{enumerate}
    \item \textbf{Raspberry Pi 5:} Serves as the primary processing unit for data collection, analysis, and storage.
    \item \textbf{OBD-II Reader:} Interfaces with the vehicle’s ECU to retrieve diagnostic data.
    \item \textbf{GPS Module:} Tracks vehicle location for route analysis and forensic applications.
    \item \textbf{Storage Devices:} SD card or external drives for secure, encrypted data storage.
    \item \textbf{Power Supply:} Reliable and portable power solutions for the Raspberry Pi and peripherals.
    \item \textbf{Display Monitor:} For debugging and system setup during development.
\end{enumerate}

\section{Software Requirements}
The software required to implement the ADAM System includes:
\begin{enumerate}
    \item \textbf{Raspberry Pi OS}  for the main processing unit.
    \item \textbf{Python}  for core logic and data processing.TensorFlow for machine learning and predictive analytics.Flask for building APIs and web-based interfaces.Cryptography libraries for secure data handling.GPS and CAN protocol libraries for location and ECU communication.
    \item \textbf{React Native} React Native for developing a cross-platform mobile application.
    \item \textbf{SQLite} a lightweight database for local storage during development.
    \item \textbf{Supabase}  for remote data synchronization and backup.
\end{enumerate}
